An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-06-19 Article/EconGrowth2-GraphsOnly.Rnw
Added text about alpha, beta, gamma, for the LINEX model.

>>>>

In the LINEX model, values of $a_0$ and $c_t$ imply values of $\alpha$, $\beta$, and $\gamma$ 
according to the following equations:

\begin{equation} \label{eq:LINEX_alpha}
  \alpha = a_0 \left( \frac{l + e}{k} \right) \;,
\end{equation}

\begin{equation} \label{eq:LINEX_beta}
  \beta = a_0 \left[ c_t \left( \frac{l}{e}\right) - \frac{l}{k} \right] \;,
\end{equation}

\noindent{}and

\begin{equation} \label{eq:LINEX_beta}
  \gamma = 1 - \alpha - \beta \;.
\end{equation}

Each curve fit implies a trajectory of $\alpha$, $\beta$, and $\gamma$ values as time proceeds.
The following graph shows China's trajectory for thermal energy ($q$):

<<LINEX_abg_traj_graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for China with thermal energy $q$.">>=
data <- fortify(OrigModels$CN$linex$`iK+iL+iQ`)
triPlot(data=data, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear")
@
